Verifying Demonstrations

### 2019-02-12 paper/identity-limits.tex
Adds conclusion to identity-system discussion

\subsection{Detecting bias}

If we do not have \iac{MPC} base solution as suggested above, we can still 
reduce the problem.
When a verifier verifies an anonymous authentication, it is clear who the 
\ac{CA} (\ie the issuer) is.
In this case the verifier can analyze whether the issuer has any incentives for 
a Sybil attack.

This is similar to detecting bias in science.
If the authors personally benefit from the results, then they are incentivized 
to bias them.
The verifiability properties of our scheme serve the same purpose as the 
methodology section of a scientific paper: anyone is able to repeat, reproduce 
and verify the results --- even if they are in distant lands.

>>>>

\section{Conclusions}

While the decentralized properties of proofs-of-personhood are appealing, it is 
hard to achieve such a scheme.
The goal is to have one identity (pseudonym) per physical person.
This goal is joint with the \enquote{birth-certificate system} which actually 
achieves the goal quite nicely in practice.
However, since the birth-certificate system relies on audit trails to function, 
it cannot deal with issuing anonymous credentials.
Thus the ideas from proof-of-personhood, where everyone must act jointly, can 
solve this problem.
To issue anonymous credentials that certify one physical person behind a 
pseudonym, all issuers must act jointly, \eg through \ac{MPC}.
